Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-26 mice_synthesizing/paper.Rmd
Update outline.

@@

- Motivation/relevance
- Synthetic data (fully/partially shortly explained)
- How can this data be generated in practice (FCS - multivariate synthetic values)
- Mice adopts FCS for missing data
- It will be shown that mice is also capable of generating multivariate synthetic data
- However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward. Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted
- Goal: explain and show how `mice` can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.

>>>>

## Introduction

- [x] What is synthetic data?
- [x] Why is it useful?
- [x] Why should it be easy to generate?
- [ ] Parallel to missing data
- [ ] If similar to missing data, then why not use `mice`?
- [ ] `mice` can only be exploited if the statistical properties are correct.
- [ ] In this paper we demonstrate a straightforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.

## Generating synthetic data with `mice`

- [ ] Explain FCS in short.
- [ ] Demonstrate procedure with `where-matrix` and explain rationale.
- [ ] Demonstrate that this is a reasonable approach, based on a figure that shows the observed and synthetic relationships side-by-side (e.g. `wgt ~ age + gen`).
- [ ] Observed values can be regarded as starting values for the imputation model. Since the observed data is used for creating the imputation models, no iterations are required. That is, the model is fixed, and not dependent on the imputed values.

## Drawing inferences from `mice` synthesized data

- [ ] What ways are there (with minimal - if any - escapes to partially/fully synthetic data).
- [ ] If based on your earlier work, cite the online reference for your simulations and give URL. No need to go into detail about it here.

### Simulation

- [ ] Simulation set-up.
- [ ] Evaluation criteria explained: the bias, coverage and CIW triangle.
- [ ] Table which demonstrates bias, coverage and CIW for all methods.

## Discussion

- [ ] Summarize findings.
- [ ] Stress that only holds for sampled data. Explain that for fully observed populations, one would need no sampling variance.
- [ ] Revisit the simplicity and the readily available solution within the `mice` workflow (if adjusted pool is required, add to mice and direct to that function).

Potentially, these approaches could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints. However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data. It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.

@@

- Motivation/relevance

- Synthetic data (fully/partially shortly explained)

- How can this data be generated in practice (FCS - multivariate synthetic values)

- Mice adopts FCS for missing data

- It will be shown that mice is also capable of generating multivariate synthetic data

- However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward. Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted

- Goal: explain and show how mice can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.
